Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-07-29 paper/main.tex
add reminder todo for abstract
introduce linebreak in title

\title{Methods for Analyzing Models of Rod-Shaped Bacteria}

@@

%###################################################################################################
\begin{abstract}
    This paper establishes the basis for a novel individual-based mechanical model of rod-shaped
    bacteria.
    It describes methods of how to obtain data from microscopic images such that they can be used
    for parameter estimation purposes.
    Furthermore, we show initial results for parameter estimates and an application of the model to
    the formation of multilayers within bacterial colonies.
\end{abstract}

>>>>

\title{Methods for Analyzing Models of\\ Rod-Shaped Bacteria}

@@

%###################################################################################################
\begin{abstract}
    \textbf{!TODO!}
    This paper establishes the basis for a novel individual-based mechanical model of rod-shaped
    bacteria.
    It describes methods of how to obtain data from microscopic images such that they can be used
    for parameter estimation purposes.
    Furthermore, we show initial results for parameter estimates and an application of the model to
    the formation of multilayers within bacterial colonies.
\end{abstract}
